---
format: html
code-fold: true
title: Quarto downloads for the last two releases
---

```{r}
#| output: false
# I know, I know.
if (!file.exists("downloads-per-day.csv")) {
    system("./gh-releases.sh")
    system("./process-gh-releases.ts > downloads-per-day.csv")
}
```

## Quarto downloads for v1.4 and v1.5, over the last 100 GitHub releases

The dataset is slightly wonky because we do not have access to daily data,
and so have to assume a constant rate of downloads from one release to the next,
as well as assume that no one downloads a specifically-older release after a newer
one exists. The latter assumption is likely fine. The former really isn't, but
it's the best we can do without tracking historical data ourselves.

```{r}
#| label: fig-downloads
#| fig-cap: Quarto Downloads from GitHub releases for the 100 most recent releases, grouped by the major version of Quarto.
#| warning: false
library(tidyverse)
library(ggplot2)
df <- read_csv("downloads-per-day.csv")
df <- df %>% mutate(date = as.Date(date))

ggplot(df, aes(x = date, y = downloads, colour = version)) +
  geom_point() + 
  labs(title = "Downloads per day",
       x = "Date",
       y = "Downloads")
```